### 2017-09-27 TF-vldb2018/sec-appendix.tex

\vspace{1ex}
\noindent
{\large \textbf{Appendix C: Extra Experiments}}
\label{sec-apd-exp}

>>>>

\vspace{1ex}
\noindent
{\large \textbf{Appendix C: Detailed Correctness \& Complexity Analysis}}
\label{sec-apd-complexity}

\noindent
{\textbf{1. Algorithm \incp (Section~\ref{subsec-Qinc})}}

The correctness of \incp \wrt $\Delta P$ is assured by
the correctness of (a) \identifyaffball (by Proposition~\ref{prop-canaffballs});
(b) \incmatch, which is assured by the correctness of \rgraphsim that has been proved, and of \patedgeinsert. Indeed, \patedgeinsert only removes
nodes that are no longer valid matches in each $M(P_{fi}, \ball{[v,r]})$;
(c) \comb, whose analysis follows the same way as for \patedgeinsert; and
(d) the early return property (by Lemma~\ref{lemma-approximation-bound}).

\vspace{-1ex}
Procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$ time, where it takes $O(2^{h}\cdot|\Delta P|)$ time to update \bfc, $O(2^{h}\cdot h)$ to do the AND-operation, and $O(||\affballsx||)$ to identify \affballsx.
%Thus, procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$.
As $h$ is typically small, \eg 2 to 5, thus \identifyaffball is in $O(|\Delta P|+||\affballsx||)$;
\patedgeinsert is in $O(|M(P_{fi}, \ball{[v,r]})|+|V_{P_{fi}}||E_{\ball{[v,r]}}|)$ time.
Indeed, the recursive process for checking invalid nodes in $M(P_{fi}, \ball{[v,r]})$ is bounded by $O(|V_{P_{fi}}||E_{\ball{[v,r]}}|)$,
and the process to update $M(P_{fi}, \ball{[v,r]})$ is bounded by the size of its changes, which is monotonically decreasing;
According to \patedgeinsert,
\comb is in $O(|\bigcup^{h}_{i=1} rM(P_{fi}\oplus\Delta P_{fi},\ball{[v,r]})|+r|V_{P\oplus \Delta P}||E_{\ball{[v,r]}}|)$ time.

\vspace{-1ex}
Putting these together, algorithm \incp is in
$O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|+r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|) + r|P \oplus \Delta P||\affballsx|$ +$|\Delta P|)$ time \wrt $\Delta P$.

\noindent
{\textbf{2. Algorithm \incd (Section~\ref{subsec-Ginc})}}

The correctness of \incd \wrt $\Delta G$ is assured by the correctness of
\identifyaffball (by Proposition~\ref{prop-affected-datainc}) and procedures \incmatch and \comb (proved along the same lines as for pattern updates).

\vspace{-1ex}
One can verify that procedure \identifyaffball is in $O(|\affballsx|)$,
\incmatch for all fragments and all \affballsx is in $O(|P||\affballsx|)$ time, and \comb is in $O(\bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|$ + $r|V_{P}||E_{\widehat{G\oplus\Delta G}}|)$ time.
Thus, algorithm \incd is in
$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx} \bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|+r|P||\affballsx|)$ time \wrt $\Delta G$.
\looseness=-1

\vspace{1ex}
\noindent
{\large \textbf{Appendix D: Extra Experiments}}
\label{sec-apd-exp}
